---
title: "Statisik - Cheat Sheet"
author: "Afdeling 11"
date: "10/12/2019"
updated: "10/12/2019"
output: 
  html_document:
    theme: united
    highlight: zenburn
    toc: true
    toc_float: true
    toc_depth: 1
    code_folding: show
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Kommandoer {.tabset .tabset-fade}
<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;border-color:#ccc;}
.tg td{font-family:Arial, sans-serif;font-size:14px;padding:10px 5px;border-style:solid;border-width:0px;overflow:hidden;word-break:normal;border-top-width:1px;border-bottom-width:1px;border-color:#ccc;color:#333;background-color:#fff;}
.tg th{font-family:Arial, sans-serif;font-size:14px;font-weight:normal;padding:10px 5px;border-style:solid;border-width:0px;overflow:hidden;word-break:normal;border-top-width:1px;border-bottom-width:1px;border-color:#ccc;color:#333;background-color:#f0f0f0;}
.tg .tg-0pky{border-color:inherit;text-align:left;vertical-align:top}
.tg .tg-btxf{background-color:#f9f9f9;border-color:inherit;text-align:left;vertical-align:top}
</style>
<table class="tg">
  <tr>
    <td class="tg-0pky">Females(x)</td>
    <td class="tg-btxf">2474</td>
    <td class="tg-0pky">2547</td>
    <td class="tg-btxf">2830</td>
    <td class="tg-0pky">3219</td>
    <td class="tg-btxf">3429</td>
    <td class="tg-0pky">3448</td>
    <td class="tg-btxf">3677<br></td>
    <td class="tg-0pky">3872</td>
    <td class="tg-btxf">4001</td>
    <td class="tg-0pky">4116</td>
  </tr>
  <tr>
    <td class="tg-0pky">Males(y)</td>
    <td class="tg-btxf">2844</td>
    <td class="tg-0pky">2863</td>
    <td class="tg-btxf">2963</td>
    <td class="tg-0pky">3239</td>
    <td class="tg-btxf">3379</td>
    <td class="tg-0pky">3449</td>
    <td class="tg-btxf">3582</td>
    <td class="tg-0pky">3926</td>
    <td class="tg-btxf">4151</td>
    <td class="tg-0pky">4356</td>
  </tr>
</table>
```{r}
x <- c(2474, 2547, 2830, 3219, 3429, 3448, 3677, 3872, 4001, 4116)
y <- c(2844, 2863, 2963, 3239, 3379, 3449, 3582, 3926, 4151, 4356)
```
## Symboler

## Sample Mean
mean()
```{r}
mean(x)
mean(y)
```
## Variance
var()
```{r}
var(x)
var(y)
```
## Standard Deviation
sd()
```{r}
sd(x)
sd(y)
```
## Quartiles / Quantile
quantile()
```{r}
quantile(x)
quantile(y)
```
## Boxplot
boxplot()<br/>
single
```{r}
boxplot(x, col = 2)
```

multiple
```{r}
boxplot(list(x,y), col = 2:3)
```

## Coefficient of variations
sd() / mean()<br/>
Kan skrives sådan for at få direkte i procent:<br/>
(sd() / mean())*100
```{r}
(sd(x)/mean(x))*100
sd(y)/mean(y)
```

## Median
median()
```{r}
median(x)
median(y)
```

##  Sample Coveriance
cov()
```{r}
cov(x, y)
```

## Sample Correlation
cor()
```{r}
cor(x, y)
```

## Binomial Distribution{.tabset .tabset-fade}
### dbinom
```{r}
dbinom(4, size = 10, prob = 0.6)*100
```
I dette sammenhæng, er det chancen for succes, når man skal have præcis 4 succeser ud af 10 forsøg med en succes chance på 60%

### pbinom
```{r}
## P(X <= 5) 5 eller under successer
pbinom(5, size = 10, prob = 0.6)*100

## P(X < 5) under 5 successer
pbinom(4, size = 10, prob = 0.6)*100

## P(X > 4) over 4 successer
(1 - pbinom(4, size = 10, prob = 0.6))*100

## P(X = 5) præcis 5 successer
(pbinom(5, size = 10, prob = 0.6) - pbinom(4, size = 10, prob = 0.6))*100
```

## Poisson Distribution {.tabset .tabset-fade}
### dpois
```{r}
dpois(4, lambda  = 3)
```
I dette sammenhæng, er det chancen for at få 4 events per interval, når gennemsnittet(mean) per interval er 3 events

### ppois
```{r}
## P(X <= 5)
ppois(5, lambda  = 3)

## P(X < 5)
ppois(4, lambda  = 3)

## P(X > 4)
1 - ppois(4, lambda  = 3)

## P(X = 5)
ppois(5, lambda  = 3) - ppois(4, lambda  = 3)
```

## Hypergeometric Distribution
```{r}

```




# Opgaver {.tabset .tabset-fade}

## Afhængige variabel og forklarende variabel i model

<p>For at undersøge downloadhastigheden ved en arbejdsstation har man målt downloadtiderne (i sekunder) for 53 filer af forskellige størrelser ( m˚alt i MB). Downloadtiderne er gemt i vektorentime i R, mens de tilsvarende filstørrelser er gemt i vektoren size. Desuden er følgende kodeblevet kørt i R:</p>

<pre>
  <code>
    logtime <- log(time)
    model1<- lm(logtime ~ size)
    summary(model1)
    
    ##
    ## Call:
    ## lm(formula = logtime ~ s ize )
    ##
    ## Residuals:
    ## Min 1Q Median 3Q Max
    ## -2.571 -0.673 0.132 0.745 2. 1 90
    ##
    ## Coefficients:
    ## Estimate Std. Error t value P r( > |t |)
    ## (Intercept) -0.109 0.482 -0.23 0.82
    ## size 0.127 0.023 5.50 1.2e-06 ***
    ## ---
    ## Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
    ##
    ## Residual standard error: 0.979 on 51 degrees of freedom
    ## Multiple R-squared: 0.372,Adjusted R-squared: 0.36
    ## F-statistic: 30.2 on 1 a nd 51 DF, p-va l ue : 1.25e-06
  </code>
</pre>

<p>
  The statistical model given by model1 is a linear regression model of the form
</p>

<pre style="text-align:center;">Yi= β0+ β1xi+ εi,</pre>

<p>
  where εi, i = 1, . . . , 53, are assumed to be independent and identically N(0, σ2) distributed
</p>

<p>Identify the dependent variable and the explanatory variable in the model given by model1.</p>


<ol>
  <li>Download time is the dependent variable. File size is the explanatory variable</li>
  <li>File size is the dependent varia b l e. The log arithm of download time is the explanatory variable</li>
  <li>Download time is the explanatory variable. File size is the dependent variable.</li>
  <li><b>File size is the explanatory variable. The logarithm of download time is the dependent variable.</b></li>
  <li>As (the logarithm of) download time depends on file size, both file size and the logarithm of download size are dependent variables. There is no explanatory variable in the model.</li>
</ol>


<h3>FACIT</h3>
<p>The variable to the left of the tilde (∼) in the R code corresponds to the dependent variable Yi, while the variable to the right of the tilde corresponds to the explanatory variable xi</p>

## 90% interval prediction (kender mean og var)

<p>The following code was also executed in R:</p>

<pre>
  <code>
    mean(size)
    
    ## [1] 20.088
    
    (53-1)*var(size)
    
    ## [1] 1807.6
  </code>
</pre>

<p>
  
</p>